An In-Cloud Backup System With Deduplication for VM Snapshot

### 2012-08-25 snapshot_system/design.tex
Append store chapter

@@

\item {\em Backup speed}
456
\end{enumerate}
\subsection{Architecture Overview}

@@

Thus the estimation of CDS coverage is $S=S_0+S_s+S_u=0.58$, with the size of CDS to be no more than $(200 + 0.006*D*N)$ GB.
In a VM cluster of 100 machines, with 25 VMs on each physical machine, the size of CDS is 800 GB in total, or 8 GB per machine.
The total size of CDS index would be 8 GB, which will cost 80 MB memory on each machine. 
\subsection{Append Store}

>>>>

Overall, our contributions are:
\begin{enumerate}
\item {\em CDS. parallelism, localized}
We designed a highly efficient global deduplication scheme using common data between VMs as the primary
deduplication target, which adopts to our resource-constrained production environment very well. We developed a fast
approxmation algorithm to extract the commonly used data from VM snapshot backups.

\item {\em Append Store.}
We address the problem of managing billions of small variable-sized data objects by building an append store
on top of our distributed file system (DFS). We carefully designed an efficient index data structure to 
optimize large sequential read/write requests, while minimize the cost of key to object location conversion.

\item {\em Fast Data Deletion.}
Traditional deletion in deduplication systems involves reference counting, either online or offline. Both ways
are costly due to the sharing of large amount of data objects.
We avoid this cost of data deletion with an approxmation deletion method using bloom filters.

\item {\em Fault-tolerant.}
Golbal deduplication brings data sharing across different users VM snapshots, therefore a single failure
on some data can break many VMs' snapshots. We avoid such all-to-all data dependency by restricting
the cross VM data sharing with the CDS. By taking extra care of protecting CDS data, 
the overall degree of fault tolerancy is guaranteed.

\end{enumerate}

@@

\item {\em Backup speed}

\end{enumerate}
\subsection{Architecture Overview}
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
based on Xen~\cite{Xen2003}. A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of VMs.

A GFS-like distributed file system holds the responsibility of managing physical disk storage
in the cloud. All data needed for VM services, which include runtime VM disk images and snapshot backup data,
reside in this distributed file system.
During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
copies the corresponding pre-configured base VM image to her VM as the OS disk, 
and an empty data disk is created and mounted onto her VM as well. 
All these virtual disks are represented as virtual machine image files in our
underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
disks is tunneled by the virtual device driver (called TapDisk\cite{Warfield2005} at Xen). To avoid network latency and congestion, 
our distributed file system place the primary replica of VM's 
image files at physical machine of VM instance.
During snapshot backup, concurrent disk write is logged 
to ensure a consistent snapshot version is captured.

Figure~\ref{fig:arch} shows the architecture view of our snapshot service
at each node. The snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
The inner-VM  deduplication is conducted by the broker to access meta data in the snapshot data store
and we discuss this in details in Section~\ref{sect:innerVM}.
The cross-VM deduplication is conducted by the broker to access 
a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
whose block hash index is stored in a distributed memory cache. 
\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
  \epsfig{file=images/arch.eps, width=3.9in}
  \caption{Snapshot backup architecture of each node.}
  \label{fig:arch}
\end{figure}
The snapshot store 
supports data access operations such as \emph{get}, \emph{put} and \emph{delete}.
Other operations include data block traverse and resource usage report.
The snapshot data does not need to be
co-located with VM instances, and in fact they can even live in a different cluster to improve the 
data reliability: when one cluster is not available, we are still able to restore its VMs from another cluster which
holds its snapshot data. 
%to reduce the impact to our users.
%Get interface accepts a piece of data, write it to the underline data file, and return
%a reference to the caller. This reference then can be used in the put interface to
%retrive or delete the data, thus the caller of put interface must preserve the
%data reference for future use. 
%In addition to above standand data access operations, the snapshot service also supports
%\emph{scan} and \emph{quota} methods. Scan allows us to traverse all the data blocks of each VM
%in the snapshot store, and quota is used to acknowledge user how much space he
%has actually used.

Under the hood of snapshot store, it organizes and operates snapshot data 
in the distributed file system. We let each virtual disk has its own snapshot store, 
and no data is shared between
any two snapshot stores, thus achieve great fault isolation. For those selected popular data
that shared by many VM snapshot stores, we could easily increase its availability by having more replications.
%Since all the underline data structures is append only,
%upon a delete request, the corresponding data will only be marked rather than being deleted.
%A compaction will take place when deleted data has accumulated to a certain threshold, thus 
%reclaiming the disk space .

@@

Thus the estimation of CDS coverage is $S=S_0+S_s+S_u=0.58$, with the size of CDS to be no more than $(200 + 0.006*D*N)$ GB.
In a VM cluster of 100 machines, with 25 VMs on each physical machine, the size of CDS is 800 GB in total, or 8 GB per machine.
The total size of CDS index would be 8 GB, which will cost 80 MB memory on each machine.

\subsection{Append Store}
